---
title: "Alcohol vs Seat choice"
author: "Jason Leon"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))
```

  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
In the data it shows that the people that in the middle are drinking a lot more then the people im the back and the front. Also in the data you can see that min all equals 0 but in the median it shows that the back have 4 and the front has 0 and the middle has 1. Thats a hugh difference. most of the people are sitting in the middle which is 83 and the rest and evened out in the back and the front and you can find that in the letter "n".

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

```{r}
# Load the necessary library
library(stats)

# Perform ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
summary(anova_result)
```

```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)
```


## Conclusions
In conclusions today we used chat gpt to make us a ggplot and then answer with what we saw on the data and explain on it for an answer. Then we answered the numerical summary and the inferential tests which we had to look at three charts.

